---
title: "Creating plots in R with 'ggplot'"
author: "David La Puma"
date: "6/26/2020"
output: html_document
---

# Plots with ggplot2

# Get them libraries loaded
```{r echo=FALSE}
library(tidyverse)
library(readxl)
library(here)
```

# Read CSV

```{r}
ca_np <- read_csv(here("data", "ca_np.csv"))
```

# Read Excel

```{r}
ci_np <- read_excel(here("data","ci_np.xlsx"))
names(ci_np)
```

To create a bare-bones ggplot graph, we need to tell R three basic things:

1. We’re using ggplot2::ggplot()
2. Data we’re using & variables we’re plotting (i.e., what is x and/or y?)
3. What type of graph we’re making (the type of geom)

Generally, that structure will look like this:

```{r}
gg_base <- ggplot(data = ci_np, aes(x = year, y = visitors))

gg_base + geom_line()
```
```{r}
gg_base + geom_point()
```

```{r}
gg_base + geom_point() + geom_line()
```

```{r}
gg_base + geom_col()
```

```{r}
gg_base + geom_area()
```

First, we’ll customize some aesthetics (e.g. colors, styles, axis labels, etc.) of our graphs based on non-variable values.

We can change the aesthetics of elements in a ggplot graph by adding arguments within the layer where that element is created.

Some common arguments we’ll use first are:

* color = or colour =: update point or line colors
* fill =: update fill color for objects with areas
* linetype =: update the line type (dashed, long dash, etc.)
* pch =: update the point style
* size =: update the element size (e.g. of points or line thickness)
* alpha =: update element opacity (1 = opaque, 0 = transparent)

```{r}
gg_base + geom_line(
  color = "purple"
)
```

```{r}
gg_base + 
  geom_point(
    aes(size = visitors,
        color = visitors),
    alpha = 0.5
)
```

```{r}
gg_base + 
  geom_col(
    aes(color = visitors)
)
```


```{r}
ggplot(data = ca_np, aes(x = year, y = visitors, group = park_name)) +
  geom_line()
```

```{r}
gg_np <- ggplot(data = ca_np, aes(x = year, y = visitors, group = park_name)) +
  geom_line()
```

```{r}
gg_np +
  geom_line(show.legend = FALSE) +
  theme_light() + 
  labs(x = "year", y = "annual visitors") +
  facet_wrap(~ park_name)

#ggsave(here("figures", "np_graph.png"), dpi = 300, width = 10)
```
# Read in Archbold Node health reports

```{r}
archNodeHealth <- read_csv(here("data", "arch_station-health-data.merged.2020-06-26_204438.csv"))
```
```{r}
gg_archNode <- ggplot(data = archNodeHealth, aes(x = Time, y = Battery, group = NodeId)) +
  geom_line()
```

```{r}
gg_archNode +
  geom_line(show.legend = FALSE) +
  theme_light() + 
  labs(x = "Date", y = "Battery Voltage") +
  facet_wrap(~ NodeId)

ggsave(here("figures", "np_graph.png"), dpi = 300, width = 10)
```
```{r}
rawbeeps <- read_csv(here("data", "station-beep-data.merged.2020-06-26_215945.csv"))
```

```{r}
gg_tags <- ggplot(data = rawbeeps, aes(x = Time, y = TagId)) +
  geom_line()
```

```{r}
gg_tags +
  geom_col(show.legend = FALSE) +
  theme_light() + 
  labs(x = "TagRSSI", y = "Time") +
  facet_wrap(~ RadioId)

#ggsave(here("figures", "np_graph.png"), dpi = 300, width = 10)
```
